Latex test

### 2018-06-15 Latex test.Rmd
Mostly failing to stargazing

---
title: | 
  | Campaign Contribution Limits and Corruption: 
  | Evidence from the 50 states
author: "Mark Hand"
date: "5/23/2018"
output: pdf_document
---

Since the 1970s, the U.S. Supreme Court has frustrated efforts at campaign finance reform by maintaining that nearly all limits on political spending violate the first amendment’s protection of free speech. The Court makes only two exceptions: The state has a compelling enough interesting in preventing “corruption of the appearance of corruption” to limit political donations. But do campaign finance laws actually prevent corruption or its appearance? Using state-level data from 1990-2012 on contribution limits, corruption arrests, and media mentions of corruption, this paper employs a linear panel regression and a difference-in-differences analysis to test whether campaign contribution limits are associated with lower levels of corruption convictions or media mentions of corruption. These methods find no relationship between the presence or level of campaign finance laws and quid pro quo corruption, suggesting that would-be reformers must keep looking for evidence to support their efforts. As current challenges to contribution limits wind their way through federal courts, the answer to this question will inform the Supreme Court’s decision to uphold or strike down remaining limits on political campaign contributions.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval=FALSE, cache = TRUE, message=FALSE, warning=FALSE)
library(haven) # import .dta
suppressMessages(library("tidyverse")) # everything 
library(plm) # For linear panel regression
library(stargazer) # For regression outputs 
library(texreg) # For regression outputs

@@

\newpage 
##Introduction
<!--Shorten?-->
In 1976, the Supreme Court ruled in Buckley v. Valeo that political campaign contributions are the equivalent of free speech, and therefore protected by the first amendment. At the same time, the Court laid out one mechanism and one justification for limiting those contributions. First, it argued that more money spent doesn’t amount of “more” speech, allowing for campaign contribution dollar amount limits. Donating one dollar or $5,000 to a political campaign amounts to a speech act, the Court held, and so it is permissible to impose limits on the amount of contributions as long as contributions are not prevented. Second, having laid out the mechanism by which money in politics might be limited, the court laid out the only justification for limiting contributions that it would accept moving forward: To prevent corruption or the appearance thereof. As Kang (2012) argues, the holdings in Buckley v. Valeo provided “the basic framework of contribution limits and disclosure requirements” for the following four decades. Since Buckley v. Valeo, Congress has passed only one campaign finance law, the Bipartisan Campaign Reform Act of 2002. Better know as McCain-Feingold, the bill took aim at unlimited “soft money” contributions to political parties and expanded the Federal Election Commission’s disclosure requirements to what it called “electioneering communications,” political ads not paid for by campaigns themselves.

Apart from McCain-Feingold, for forty years all changes in the landscape of campaign finance have come from the courts, the majority being decided upon how to balance questions of free political speech versus corruption. Those rulings have often been driven by the question of corporations’ participation in the political process. In 1978, the Court extended free speech protections to corporations (First National Bank of Boston v. Bellotti). In 1986, it  and struck down efforts to restrict their expenditures to FEC-registered Political Action Committees (FEC v. Massachusetts Right to Life). Then in 1990, it upheld a ban on corporations using treasury funds to pay for issue advertisements, arguing for an extended definition of corruption, "the corrosive and distorting effects of immense aggregations of wealth that are accumulated with the help of the corporate form and that have little or no correlation to the public's support for the corporation's political ideas" (Austin v. Michigan State Chamber of Commerce, later overturned).

The passage of the McCain-Feingold in 2002 inspired a wave of challenges to campaign contributions and expenditures, driven mostly by conservative and religious groups. In 2007, the Court examined the McCain-Feingold ban on airing issue advertisements close to election. Banning such ads, the Court argued, would have a chilling effect on free speech, and it struck down the ban (FEC v. Wisconsin Right to Life). Then, in 2010, the Court issued what has become one of its most well-known rulings: In Citizens United v. FEC (2010), it struck down limits on independent expenditures by outside groups, including corporations and unions. One critical aspect of Citizens United is the establishment of the principle that, according to Justice Anthony Kennedy, “independent expenditures do not lead to, or create the appearance of, quid pro quo corruption.” The Court’s emphasis on quid pro quo corruption as the only justification for contribution limits extended the following year, as it struck down an Arizona effort to level the political playing field with matching state campaign funds (Arizona Free Enterprise Club v. Bennett, 2011).

Since 2011, the network of conservative legal groups behind Citizens United has continued to take aim at contribution limits as an unnecessary restriction of political speech, with a focus on individual contribution limits. The 1971 Federal Election Campaign Act placed a limit on the amount an individual could give to one campaign, in addition to two-year limits on the total amount an individual could give to political campaigns. In McCutcheon v. FEC (2014) James Bopp, one of the attorneys behind the Citizens United challenge, convinced the Court of the unconstitutionality of total individual limits. Another case, Holmes v. FEC (2017), targeted the distribution of individual campaign contribution across primary and general elections. In yet another, Lair v. Motl (2017), Bopp once again took aim at individual contribution limits, arguing that the state of Montana had not shown compelling evidence that campaign contribution limits decreased the risk of corruption.

The Ninth Circuit Court of Appeals upheld Montana’s campaign contribution limits, but further challenges to contribution limits are likely. Bopp said that he planned to appeal the Ninth Circuit’s ruling. Even if that fails, Bopp and other conservative groups plan to carry on. “I handle a lot of cases,” he said after the 2014 McCutcheon ruling, “and I‘m not done yet.” Supreme Court Justice Clarence Thomas laid the groundwork for future challenges in his commentary on the McCutcheon decision by arguing that more dollars did, in fact, equate to more speech. Once established, that principle supports the argument that campaign contribution dollar amount limits are a potentially unconstitutional restriction on speech (Hurley & Debenedetti 2014, Zall 2017).

##Prior Work 
<!--Add in more references--> 
Since the Buckley v. Valeo decision, a wave of scholarship has taken advantage of the campaign contribution data collected by the Federal Election Commission to examine the causes and consequences of political campaign contributions, including whether contributions buy access (not to a meaningful degree, find Welch 1982 and Langbein 1986) and the effectiveness of contributions relative to lobbying efforts (yes, according to Wright 1990). Since the 2010 Citizens United and speechnow.org decisions, another arm of scholarship has examined the flows of money to groups engaging in independent expenditures (Spencer and Wood 2014, Werner and Coleman 2014).

But lobbying, money for access, and independent expenditures all fall outside of the narrow definition of quid pro corruption that the Supreme Court considers a compelling enough state interest to justify campaign contribution limits. The scholarly research on corruption thus narrowly defined is mixed and heated. Stratmann finds evidence that donations determined votes in at least one instance (1991); he also finds that the timing of political action committees (PAC) donations suggests that corporations believe those donations do affect legislators’ votes (1998). Reacting to the absence of evidence that donations lead to favorable final votes on bills, Hall and Wayman (1990) look for and find a positive relationship between political donations and the amount of attention that legislators give to a particular issue. Other scholars, however, are not so convinced. Wright (1990) finds that once lobbying efforts are factored in, the effects of contributions on voting outcomes washes out. And it is notoriously difficult to tease out whether political donations change legislators’ minds or instead flow to legislators with established, friendly positions (Ansolabehere et al 2003).

As mentioned above, the Court is also interested in the appearance of corruption. On this score, results are more consonant: There seems to be little association between campaign spending and public trust in government (Primo 2002). Other factors, including media coverage of campaign finance law and the professionalization of legislatures, are more predictive of public perceptions of corruptions (Rosenson 2009). And while the public does seem to report viewing campaign finance as a contributor to corruption, there is not evidence that reform efforts will have an effect on those views (Persily & Lammie 2004).

One fundamental limitation of these federal level studies on campaign contributions and corruption, however, is the absence of a counterfactual: Given that contribution limits have been in place since the 1970s, it is difficult to argue what might have happened in their absence. Recent work on campaign finance has attempted to address this problem by focusing on the effects of differences in campaign finance laws at the state level. Variation across states and over time allows room for studying the causes and consequences of campaign finance limits. Studies suggest that campaign finance limits are associated with less electoral competition (Gross et al 2002, Lott 2006), but that disclosure rules and some organizational limits are associated with greater levels of government trust (Primo and Milyo 2006) and may increase the return on campaign expenditures (Stratmann 2006). As mentioned, Michael Barber’s 2016 work finds that lower limits on PAC donations relative to individual donations are associated with higher polarization.

A largely separate body of work has examined the causes and consequences of corruption at the state level. Most use the Department of Justice’s Annual Public Integrity Report, which correlate highly with state level perceptions of corruption (Walker and Calcagno 2011, Glaeser and Saks 2006, Liu & Mikesell 2014). Using that data, researchers have found evidence that political corruption leads to inflated state budgets and that the presence of casinos and subsequent corruption (Liu & Mikesell 2014, Walker & Calcagno 2013). They have also shown the absence of a link between state ethics commissions and reduced corruption (Crider and Milyo 2013). Researchers have also developed alternative measures of state level corruption, including surveys of state reporters (Boylan and Long 2003) and the recently available Transactional Records Access Clearinghouse (TRAC) database of political corruption (Cordis & Milyo 2016).

Very little work, however, has connected the literature on state-level campaign finance regulations to measures of political corruption--the one question of import to the Supreme Court as it considers the constitutionality of contribution limits. The exception to this is one 2013 working paper by Cordis and Milyo. In line with Persily and Lammie (2004), Milyo argues that campaign reform efforts have little effect on public perceptions of corruption. This paper seeks to address this gap, putting state level campaign finance data in direct conversation with state level corruption data.

##Design and Data 
<!--Add in summary statistics?-->
This paper builds upon the growing body of state-level political science research to ask the question: Are campaign contribution limits at the state level associated with lower levels of corruption? Given open debate about the proper measure of state-level corruption, this paper uses two. The first, a Corruptions Convictions Index, is the traditional measure of state level corruption, built from Department of Justice convictions data. The second, the Corruptions Reflection Index, is a new measure put forward by Dincer and Johnston (2016). I combine these measures with a third dataset from Michael Barber’s 2016 work on campaign contribution limits and political polarization; and a fourth dataset from James Alt and David Dryer Lassen, to provide controls for the full model (Alt and Lassen 2012).

Barber’s dataset is a panel of contribution limits from 1990-2012 for the lower house of every state legislature. Barber compiled this dataset from the FEC, Westlaw, and the Nation Council of State Legislatures. Each dollar amount is inflation indexed to 2010 dollar amounts, and bi-annualized. There are three different types of limits in the Barber database: Individual contribution limits, individual-to-party limits, and PAC limits. Barber utilized individual and PAC contributions in his analysis of polarization, leaving out individual-to-party limits given that party contributions typically make up less than 10% of total political fundraising; I include it this analysis to determine whether parties, rather than PACs or individuals, might be the locus of corruption as measured by our other two datasets (Barber 2016).

The second dataset comes from the Department of Justice’s “Report to Congress on the Activities and Operations of the Public Integrity Section” by way of the Institute for Corruption Studies.[^Koch]  Since 1976, the FBI has tracked political corruption at the state level, and the Corruption Convictions Index (CCI) used here includes the number of corruption convictions in a year normalized by the population in each state. This measure of corruption is widely used in academic research.

The third dataset is the Institute for Corruption Studies’ Corruption Reflections Index (CRI), put together by Dincer and Johnston for their 2016 article on state-level corruption, and which they create in response to the limitations of the Corruption Convictions. The Corruption Reflections Index represents the fraction of Associated Press stories about politics in a particular state that mention political corruption (Dincer and Johnston 2016).

The fourth dataset provides controls for the panel model. In their 2012 work examining variation in prosecutorial resources, Alt and Lassen follow Glaeser and Saks (2006) in controlling for income and education levels, size of government, legislature control, and urbanization. Alt and Lassen's dataset runs from 1976-2004. When included in the second and third models, this limits the analysis to the years from 1990-2004.

This analysis has its limitations, beginning with the datasets themselves. Barber’s state campaign contributions data lacks information about upper houses of state legislatures, which are included in both the CCI and CRI. The Corruption Convictions Index suffers from a number of issues, as outlined by Dincer and Johnston in their introduction to the Corruption Reflections Index. They argue that the CCI includes only federal data; the resources available to prosecutors varies from state to state; US Attorneys are political appointees; and the measure records only convictions, which is at best a reflection of underlying corruption.

The Corruption Reflections Index, too, has its limits: It relies on a single news source, the Associated Press. Similar to federal prosecutors’ offices, the resources available to each AP office vary. It also demonstrates high variation in the data; Utah, for example, has a mean CRI score of 0.46 and standard deviation of 0.38, in a dataset with an overall mean of 0.28 and standard deviation of 0.19. The Corruption Reflections Index also seems to assume in its name that media reports of corruption are a mere reflection of corruption, rather than an endogenous variable in the ecosystem that enables corrupt behavior. Previous work, in contrast, has argued that media have a clear bias and play an important role in shaping public perceptions of corruption (Sorauf 1987; Ansolabehere, Snowberg and Snyder 2005).

Most broadly, this analysis does not directly address the “appearance of corruption,” the second of the Supreme Court’s reasons for allowing campaign contribution limits; to do so effectively would require time series, state-level data specifically about quid pro quo corruption. It is also the case that this analysis looks to the states intentionally in order to address the issue of the counterfactual inherent in looking at federal data, it may not be the case that statewide results are generalizable to, or distinct from, what is occurring at the federal level. Finally, the period in question (1990-2004) is short enough that there may be some factor that influences corruption arrest across a meaningful portion of the dataset.

[^Koch]: N.B. According to one of the researchers’ [curricula vitae](https://about.illinoisstate.edu/odincer/Documents/CVDincerApril2016.docx), the Institute for Corruption Studies is funded in part by a grant from the Charles Koch Research Foundation. Organizations funded by Charles and David Koch are also funders of legal groups driving legal battles mentioned in the introduction, according to a [report](https://www.publicintegrity.org/2017/11/15/21279/kochs-key-among-small-group-quietly-funding-legal-assault-campaign-finance) by the Center for Public Integrity.

##Methods
### Model I: Panel Regression
Having constructed a full 1990-2012 panel dataset from these three datasets, I then run a set of time series regressions testing the relationship between contribution limits and both dependent variables, the Corruption Convictions Index and the Corruption Reflections Index.

I include three independent variables in both sets of models: Individual contribution limits, individual-to-party contribution limits, and PAC contribution limits. For each of these independent variables, I construct two variables to use in the model. The first is a dummy variable indicating whether there are contribution limits in that state in that year, coded as “0” if there are no limits and “1” if there are. The second is a continuous variable indicating the dollar amount of the limit in the state in that year. By interacting these two variables, I test two separate associations. The dummy variable tests whether there is a difference in the CCI and CRI in states with limits versus states without limits. The continuous variable tests whether higher or lower limits are associated with higher or lower CCI and CRI scores, within the group of states that have limits in a given year. After performing this transformation on all three independent variables, I test two initial sets of models: (1) Corruption Convictions Index versus campaign contribution limits in a given state-year, and (2) Corruption Reflections Index versus campaign contributions in a given state-year.

<!--
Corruption Convictions Index versus campaign contribution limits in a given state-year:

$Convictions = \alpha + \beta_{indiv.dummy} + \beta_{indiv.dummy}*\beta_{indiv.limit} + \beta_{pac.dummy} + \beta_{pac.dummy}*\beta_{pac.limit} + \beta_{indiv-to-party.dummy} + \beta_{indiv-to-party.dummy}*\beta_{indiv-to-party.limit} + \epsilon$

Corruption Reflections Index versus campaign contributions in a given state-year:

$Reflections = \alpha + \beta_{indiv.dummy} + \beta_{indiv.dummy}*\beta_{indiv.limit} + \beta_{pac.dummy} + \beta_{pac.dummy}*\beta_{pac.limit} + \beta_{indiv-to-party.dummy} + \beta_{indiv-to-party.dummy}*\beta_{indiv-to-party.limit} + \epsilon$
-->

If the model above fails to show an initial correlation, this may be due to the confounding effect of absent variables. In order to test that, I build a model of political corruption using control variables previously demonstrated to be correlated with corruption arrests, resulting in a dataset covering 1990-2004, the period of overlap between Barber's and Alt and Lassen's data. These include controlling for the size and education levels of the population, the ideology of a population, income levels and inequality, education levels, the number and relative income of government employees, and urbanization. Building a model of corruption that includes variables previously demonstrated to be correlated with corruption levels, then adding in campaign finance data, can better identify the association of campaign finance laws with corruption levels.

### Model II: Difference-in-Difference Model
<!--Add specification, formulas?-->
Even if the panel models above fail to capture correlation between state level campaign finance laws and corruption arrests, it could be the case that changes in campaign finance laws, rather than relative campaign finance limits, could be correlated with decreases in corruption. A difference-in-difference regression can help identify this by comparing the state-years in which campaign finance laws changed to state-years where they remained constant. If tighter campaign finance laws are correlated with lower corruption levels, then a change in one year should lead to lower corruption convictions in the years following.

##Results 
### Modeling campaign limits and corruption arrests 
The results of the initial panel regression reveal no correlation between state-level campaign contribution limits and corruption, with one exception: There is a statistically significant relationship between the presence of individual-to-party limits and the Corruption Reflections Index.

The first set of models (below) measures the association of various campaign contribution limits with the Corruption Convictions Index. The sign of each coefficient is negative, indicating that the presence of limits is associated with lower corruption levels, but that where limits exist, higher (weaker) donation limits are associated with lower levels of corruption. None of those results are significant at the p<0.05 level, however, meaning that we cannot claim their effect is statistically distinguishable from zero. I interpret these results as showing no relationship between the presence or amount of state-level contribution limits and levels of corruption as measured by the Corruption Convictions Index.

@@

```{r stargazer CCI latex, results="asis", include=F}
stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,
  type="latex", 
  title = "Are campaign limits and corruption convictions correlated?",
  dep.var.labels = c("Corruption Convictions Index"),
  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
```

\begin{table}[!htbp] \centering 
  \caption{Are campaign limits and corruption convictions correlated?} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{Corruption Convictions Index} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
 Individual limit amounts & $-$0.00004 &  &  & $-$0.00003 \\ 
  & (0.00005) &  &  & (0.0001) \\ 
  & & & & \\ 
 Individual limits (dummy) & $-$4.021 &  &  & $-$2.989 \\ 
  & (4.572) &  &  & (5.076) \\ 
  & & & & \\ 
 Individual-to-party limit amount &  & $-$0.00000 &  & 0.00000 \\ 
  &  & (0.00001) &  & (0.00001) \\ 
  & & & & \\ 
 Individual-to-party limits (dummy) &  & $-$0.019 &  & 0.363 \\ 
  &  & (0.626) &  & (0.684) \\ 
  & & & & \\ 
 PAC limit amounts &  &  & $-$0.00002 & $-$0.00002 \\ 
  &  &  & (0.00002) & (0.00002) \\ 
  & & & & \\ 
 PAC limits (dummy) &  &  & $-$1.762 & $-$1.339 \\ 
  &  &  & (1.519) & (1.743) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Observations & 1,149 & 1,149 & 1,149 & 1,149 \\ 
R$^{2}$ & 0.002 & 0.00002 & 0.002 & 0.002 \\ 
Adjusted R$^{2}$ & $-$0.066 & $-$0.068 & $-$0.066 & $-$0.069 \\ 
F Statistic & 0.826 (df = 2; 1075) & 0.012 (df = 2; 1075) & 0.843 (df = 2; 1075) & 0.426 (df = 6; 1071) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

The second set of models (below) also fails to find a relationship between state-level campaign contribution limits and media mentions of corruption as measured by the Corruption Reflections Index, with one exception: The presence of limits on what an individual can give to a party is associated with a 0.087 point decline in the Corruption Reflection Index. The Corruption Reflections Index operates on a scale of zero to one (with a few outlying exceptions), meaning that the presence of individual-to-party limits is associated with an 8.7% point decrease in the index.

@@

```{r stargazer CRI latex, results="asis", include=F}
stargazer(CRIreg1, CRIreg2, CRIreg3, CRIreg5,
  title = "Are campaign limits and corruption reflections correlated?",
  dep.var.labels = c("Corruption Reflections Index"),
  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
```

\begin{table}[!htbp] \centering 
  \caption{Are campaign limits and corruption reflections correlated?} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{Corruption Reflections Index} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
 Individual limit amounts & $-$0.00000 &  &  & $-$0.00000 \\ 
  & (0.00000) &  &  & (0.00000) \\ 
  & & & & \\ 
 Individual limits (dummy) & $-$0.316 &  &  & $-$0.328 \\ 
  & (0.257) &  &  & (0.284) \\ 
  & & & & \\ 
 Individual-to-party limit amount &  & $-$0.00000 &  & $-$0.00000 \\ 
  &  & (0.00000) &  & (0.00000) \\ 
  & & & & \\ 
 Individual-to-party limits (dummy) &  & $-$0.087$^{**}$ &  & $-$0.099$^{***}$ \\ 
  &  & (0.035) &  & (0.038) \\ 
  & & & & \\ 
 PAC limit amounts &  &  & 0.00000 & 0.00000 \\ 
  &  &  & (0.00000) & (0.00000) \\ 
  & & & & \\ 
 PAC limits (dummy) &  &  & 0.009 & 0.096 \\ 
  &  &  & (0.085) & (0.098) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Observations & 1,150 & 1,150 & 1,150 & 1,150 \\ 
R$^{2}$ & 0.002 & 0.007 & 0.0001 & 0.010 \\ 
Adjusted R$^{2}$ & $-$0.066 & $-$0.060 & $-$0.068 & $-$0.061 \\ 
F Statistic & 0.842 (df = 2; 1076) & 3.937$^{**}$ (df = 2; 1076) & 0.037 (df = 2; 1076) & 1.858$^{*}$ (df = 6; 1072) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

The third set of models incorporates a number of control variables in order to isolate the effect of campaign finance laws on corruption arrest levels. As in the models above, the only correlation significant at the p<0.05 level is the presence of limits on what an individual can give to a party; again, the presence of limits in what an individual can give to a party is associated with a decline in the Corruption Reflections Index.

@@

```{r stargazer controlled panel latex, results="asis", include=F}
stargazer(CCIcontrol01,CCIcontrol02,CRIcontrol01,CRIcontrol02,
  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
  covariate.labels=c("Divided government", "Binding one-term limit"," Binding two-term limit","Real per capita income (thousands)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues (thousands)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)","Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)")
  )
```

Too big to include?

\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{2}{c}{Corruption Convictions Index} & \multicolumn{2}{c}{Corruption Reflections Index} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
 Divided government & $-$0.371$^{*}$ & $-$0.332 & 0.012 & 0.014 \\ 
  & (0.208) & (0.211) & (0.014) & (0.014) \\ 
  & & & & \\ 
 Binding one-term limit & 0.228 & $-$0.294 & 0.056 & 0.112 \\ 
  & (1.399) & (1.494) & (0.093) & (0.098) \\ 
  & & & & \\ 
  Binding two-term limit & 0.013 & 0.048 & 0.002 & $-$0.0004 \\ 
  & (0.232) & (0.234) & (0.015) & (0.015) \\ 
  & & & & \\ 
 Real per capita income (thousands) & $-$0.001$^{**}$ & $-$0.001$^{**}$ & 0.00001 & 0.00001 \\ 
  & (0.0002) & (0.0002) & (0.00002) & (0.00002) \\ 
  & & & & \\ 
 AUSAs per million population & 0.064 & 0.077 & 0.0003 & $-$0.001 \\ 
  & (0.060) & (0.061) & (0.004) & (0.004) \\ 
  & & & & \\ 
 Unemployment & 0.007 & 0.029 & 0.015 & 0.013 \\ 
  & (0.155) & (0.161) & (0.010) & (0.011) \\ 
  & & & & \\ 
 Citizen ideology measure & $-$0.001 & 0.001 & $-$0.001 & $-$0.001 \\ 
  & (0.020) & (0.021) & (0.001) & (0.001) \\ 
  & & & & \\ 
 Percent high school graduates & $-$2.187 & $-$1.955 & $-$0.707 & $-$0.901$^{*}$ \\ 
  & (7.236) & (7.455) & (0.477) & (0.488) \\ 
  & & & & \\ 
 Real per capita gov revenues (thousands) & 0.002 & 0.002$^{*}$ & 0.0002$^{**}$ & 0.0002$^{***}$ \\ 
  & (0.001) & (0.001) & (0.0001) & (0.0001) \\ 
  & & & & \\ 
 Inequality: Male wages & 0.131$^{***}$ & 0.125$^{***}$ & $-$0.004 & $-$0.003 \\ 
  & (0.048) & (0.048) & (0.003) & (0.003) \\ 
  & & & & \\ 
 Relative government wages & 32.384 & 28.128 & 4.163 & 7.262$^{**}$ \\ 
  & (45.126) & (47.558) & (2.984) & (3.123) \\ 
  & & & & \\ 
 Urbanization & 0.074 & 0.073 & $-$0.013$^{*}$ & $-$0.016$^{**}$ \\ 
  & (0.114) & (0.115) & (0.007) & (0.008) \\ 
  & & & & \\ 
 Log of population (millions) & 3.883 & 2.988 & 0.098 & 0.018 \\ 
  & (3.032) & (3.231) & (0.200) & (0.212) \\ 
  & & & & \\ 
 Individual limit amounts &  & 0.0001 &  & $-$0.00001 \\ 
  &  & (0.0001) &  & (0.00001) \\ 
  & & & & \\ 
 Individual limits (dummy) &  & 8.012 &  & $-$0.561 \\ 
  &  & (8.409) &  & (0.550) \\ 
  & & & & \\ 
 Individual-to-party limit amount &  & 0.00000 &  & 0.00000 \\ 
  &  & (0.00001) &  & (0.00000) \\ 
  & & & & \\ 
 Individual-to-party limits (dummy) &  & 0.260 &  & $-$0.111$^{**}$ \\ 
  &  & (0.744) &  & (0.049) \\ 
  & & & & \\ 
 PAC limit amounts &  & $-$0.00002 &  & $-$0.00000 \\ 
  &  & (0.00004) &  & (0.00000) \\ 
  & & & & \\ 
 PAC limits (dummy) &  & $-$1.547 &  & $-$0.192 \\ 
  &  & (3.176) &  & (0.209) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Observations & 671 & 671 & 672 & 672 \\ 
R$^{2}$ & 0.038 & 0.043 & 0.029 & 0.047 \\ 
Adjusted R$^{2}$ & $-$0.080 & $-$0.084 & $-$0.090 & $-$0.080 \\ 
F Statistic & 1.818$^{**}$ (df = 13; 597) & 1.413 (df = 19; 591) & 1.368 (df = 13; 598) & 1.549$^{*}$ (df = 19; 592) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

### Modeling changes in campaign limits and corruption arrests

The final set of models is a set of difference-in-difference models designed to isolate the effect of changes in campaign finance laws on corruption arrests. None of the models find correlation between campagin finance limits and either corruption convictions or corruption reflections.

### INSERT FIGURE 4 HERE
```{r stargazer DiD}
stargazer(CCIDID01, CCIDID02, CCIDID03, CRIDID01, CRIDID02, CRIDID03,
  type="text", 
  title = "Do changes in limits lead to lower levels of corruption?",
  out="collateral/DiD.htm",
  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
  covariate.labels=c("Individual limits removed","Individual limits imposed","Individual limit amount","Individual limits removed*amount","Individual limits imposed*amount",
                     "PAC limits removed","PAC limits imposed","PAC limit amount","PAC limits removed*amount","PAC limits imposed*amount",
                     "Individual-to-party limits removed","Individual-to-party limits imposed","Individual-to-party limit amount","Individual-to-party limits removed*amount","Individual-to-party limits imposed*amount"))

@@

```{r stargazer DiD latex, results="asis", include=F}
stargazer(CCIDID01, CCIDID02, CCIDID03, CRIDID01, CRIDID02, CRIDID03,
  title = "Do changes in limits lead to lower levels of corruption?",
  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
  covariate.labels=c("Individual limits removed","Individual limits imposed","Individual limit amount","Individual limits removed*amount","Individual limits imposed*amount",
                     "PAC limits removed","PAC limits imposed","PAC limit amount","PAC limits removed*amount","PAC limits imposed*amount",
                     "Individual-to-party limits removed","Individual-to-party limits imposed","Individual-to-party limit amount","Individual-to-party limits removed*amount","Individual-to-party limits imposed*amount"))

>>>>

---
title: "Latex test"
author: "Mark Hand"
date: "6/15/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval=FALSE, cache = TRUE, message=FALSE, warning=FALSE)
library(haven) # import .dta
suppressMessages(library("tidyverse")) # everything 
library(plm) # For linear panel regression
library(stargazer) # For regression outputs #fail 
library(texreg) # For regression outputs #fail 
library(kableExtra) # For regression outputs 
library(broom) # Because Matt Worthington said so 
library(knitr) # Because Matt Worthington said so

@@

@@

```{r stargazer CCI latex, results="asis", eval=T}
stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,
  type="latex", 
  title = "Are campaign limits and corruption convictions correlated?",
  dep.var.labels = c("Corruption Convictions Index"),
  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
```

@@

```{r stargazer CRI latex, results="asis", eval=T}
stargazer(CRIreg1, CRIreg2, CRIreg3, CRIreg5,
  title = "Are campaign limits and corruption reflections correlated?",
  dep.var.labels = c("Corruption Reflections Index"),
  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
```

@@

```{r stargazer controlled panel latex, results="asis", eval=T}
stargazer(CCIcontrol01,CCIcontrol02,CRIcontrol01,CRIcontrol02,
  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
  covariate.labels=c("Divided government", "Binding one-term limit"," Binding two-term limit","Real per capita income (thousands)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues (thousands)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)","Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)")
  )
```

```{r stargazer DiD}
stargazer(CCIDID01, CCIDID02, CCIDID03, CRIDID01, CRIDID02, CRIDID03,
  type="text", 
  title = "Do changes in limits lead to lower levels of corruption?",
  out="collateral/DiD.htm",
  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
  covariate.labels=c("Individual limits removed","Individual limits imposed","Individual limit amount","Individual limits removed*amount","Individual limits imposed*amount",
                     "PAC limits removed","PAC limits imposed","PAC limit amount","PAC limits removed*amount","PAC limits imposed*amount",
                     "Individual-to-party limits removed","Individual-to-party limits imposed","Individual-to-party limit amount","Individual-to-party limits removed*amount","Individual-to-party limits imposed*amount"))

@@

```{r stargazer DiD latex, results="asis", eval=T}
stargazer(CCIDID01, CCIDID02, CCIDID03, CRIDID01, CRIDID02, CRIDID03,
  title = "Do changes in limits lead to lower levels of corruption?",
  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
  covariate.labels=c("Individual limits removed","Individual limits imposed","Individual limit amount","Individual limits removed*amount","Individual limits imposed*amount",
                     "PAC limits removed","PAC limits imposed","PAC limit amount","PAC limits removed*amount","PAC limits imposed*amount",
                     "Individual-to-party limits removed","Individual-to-party limits imposed","Individual-to-party limit amount","Individual-to-party limits removed*amount","Individual-to-party limits imposed*amount"))
